\chapter{Introduction}

\section{What is a \RS?}

A \RS is not a surface with a Riemannian metric,
but it is a one-dimensional complex manifold.

% TODO: Condense and move rigorous def into chapter 3
\begin{defi}
	A \defn{manifold} is a topological space
	which is Hausdorff, second-countable and locally Euclidean
	together with an atlas \(\mathcal A\)
	of charts \(\alpha = (\U\alpha, \uphi\alpha)\)
	consisting of an open set \(\U\alpha\)
	and a map
	\[\uphi\alpha\colon \U\alpha \to \R^n\]
	which is homeomorphic
	onto its image \(\uphi\alpha[\U\alpha] \subsetopen \R^n\)
	each
	and such that \(M = \bigcup_\alpha \U\alpha\) is covered.

	When the \defn{transition maps}
	\begin{align*}
		\trans\alpha\beta
		\coloneqq \uphi\beta\circ{\uphi\alpha}^{-1}
		\colon
		    \uphi\alpha[\U\alpha\cap\U\beta]
	        \to \uphi\beta [\U\alpha\cap\U\beta]
	\end{align*}
	are all in a class
	\(C \subseteq \{f\colon U \to \R^n \:\vert\: U \subsetopen \R^n\}\),
	we call \((M, \mathcal A)\) a \(C\)-manifold.
\end{defi}

% TODO: Cool graphics

By identifying \(\R^2 = \C\)
and setting
\[	\Hol \coloneqq
	\{f\colon U \to \C \:\vert\:
		\text{\(U \subsetopen \C\),
		\(f\) holomorphic}
	\}
\]
we obtain the definition of a \RS.

\begin{defi}
	A \defn{\RS} is a \(\Hol\)-manifold.
\end{defi}

% Why not “complex curve”?
Since we have
\(\Hol \subset \{f \in \smooth(U, \R^2) \:\vert\: U \subsetopen \R^2\}\),
any \RS is a smooth two-dimensional real manifold,
\ie a surface.

\section{Why is a \RS?}

We give a few, increasingly complex\footnote{pun intended}
examples of \RSs.

\begin{bsp}
Most likely the easiest and most well-known constructions of \RSs
are the following four.
\begin{itemize}
\item \(\C\) is a \RS.
\item Any open subset \(U \subsetopen M\) of a \RS \(M\) is a \RS itself.
\item The Riemann Sphere \(\hat\C = \C \cup \{\infty\} = \S^2\) is a \RS.
	Topologically, it is the Alexandroff compactification of \(\C\).
\item Suitable quotients of \RSs are \RSs,
	\eg the Torus \(\C / (\Z + \i\Z)\).
	% TODO: Cool graphics
\end{itemize}
\end{bsp}

\begin{bsp}
	We can associate \RSs to holomorphic functions.
	For example,
	we would like to define the natural logarithm
	of any \(z = r\e^{\i\theta} \neq 0\)
	with \(r > 0\) and \(\theta \in \R\) by
	\[
		\ln(z)
		= \ln(r\e^{\i\theta})
		= \ln(r) + \ln(\e^{\i\theta})
		= \ln(r) + \i\theta,
	\]
	However, there is a problem:
	For any \(z \neq 0\),
	the argument \(\theta\) is only well-defined modulo \(2\pi\).
	Choosing any system of representatives
	to obtain a total function \(\ln\colon \C^* \to \C\)
	is neither natural nor will it ever lead to a continuous function.

	This can be fixed in two ways.
	For one, we can think of the logarithm as being multi-valued,
	obtaining
	\[
		\ln(\i)
		= \i\frac\pi2+2\pi\i\Z
		= \left\{
			\frac12\pi\i, \frac52\pi\i,
			-\frac32\pi\i, \frac92\pi\i,
			-\frac72\pi\i, \dots
		\right\}.
	\]
	For the other,
	we need \RSs to “unfold the complex plane”.
\end{bsp}

\begin{bsp}
	Projective non-singular curves are \RSs.
	For example, we can take the polynomial equation
	\[y^2 = x^3+ax+b\]
	with parameters \(a\) and \(b\)
	and study the set of solutions \(S \subseteq \C^2 \subseteq \Proj\C2\),
	where the latter is a holomorphic manifold of complex dimension \(2\).
	In the language of algebraic geometry,
	\(S\) is an algebraic subvariety of \(\Proj\C2\)
	and whenever \(S\) has no singularities,
	it is a \RS.
\end{bsp}

\section{How is a \RS?}

To conclude our initial tour of \RSs,
we consider alternative ways
to look at or define this class of spaces.
A \RS is a real surface with some extra structure.
There are various way to characterize this extra structure:
\begin{description}
\item[As defined] The holomorphic structure can be given with an atlas.
\item[Algebraically] Any compact \RS
	corresponds to a non-singular projective curve.
\item[Conformal] Two Riemannian metrics are considered conformal
	it they only differ by a (pointwise) rescaling
	or~-- equivalently~-- if they measure the same angles.
	A \RS can be equivalently given
	as a real surface together with a conformal class of Riemann metrics.
\item[Hyperbolic] Using the Poincaré uniformization theorem,
	it is possible to show
	that “nearly all” Riemann surfaces are hyperbolic,
	\ie have negative Gauß curvature,
	which means that they are quotients of the hyperbolic space \(\H^2\).
\end{description}
